DRAFT W GRAVEL! Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-31 Child-Metrics-Region.Rmd
many updates not tracked

[comment]: # creates a section for a smaller geo passed with details
[comment]: # loops over a number i referencing the geo in breakdowns tibble
[comment]: # called from Draft-Ped-Metrics-Example.Rmd

@@

```{r bdtext-{{i}}}
intro_text <- paste0("Kitsap County has ",
                    ifelse(!has_points, # poly only 
                           paste(nrow(b_polydf), 
                                 b_name)
                           , # now the ones with points
                           paste0(nrow(b_pointdf), 
                                  " ",
                                  b_name, 
                                  "; however, only ",
                                  nrow(b_polydf),
                                  " are outside of city limits. Here they are shown with a 30 minute walking distance")
                           ),".")

title_text <- paste("Kitsap County",b_name)
subtitle_text <- ifelse(b_name %ni% c("Commissioner Districts","LAMIRDs"),
                        "only showing those in the unincorporated county","")
caption_text <- paste("Data source:",breakdowns$data_source[i])

@@

```{r bdmap-{{i}}}
#| fig.width = 8,
#| fig.height = 8,
#| out.width = '100%',
#| dpi = 96
#| 
kitsap +
  geom_sf(data = b_polydf, aes(fill = eval(as.symbol(b_idcol))), 
          lwd = 0, alpha = 0.6) +
  {if (has_points) geom_sf(data = b_pointdf, aes(color = 1), 
                           color = "black", show.legend = FALSE) } +
  theme_void() +
  labs(title = title_text,
       subtitle = subtitle_text,
       caption = caption_text,
       fill = b_name)

@@

```{r bdloop-{{i}}, include=FALSE, echo=FALSE, cache = TRUE}

expanded_child <- lapply(
    b_items,
    function(x) {
      knitr::knit_expand(file = "child_single_geo_in_region.Rmd",
                                current_geo = x )
    })

>>>>

@@

```{r bdtext-{{i}}}
intro_text <- paste0("Kitsap County has ",
                    ifelse(!has_points, # poly only 
                           paste(nrow(b_polydf), 
                                 b_name)
                           , # now the ones with points
                           paste0(nrow(b_pointdf), 
                                  " ",
                                  b_name, 
                                  "; however, only ",
                                  nrow(b_polydf),
                                  " are outside of city limits. Here they are shown with a 15 minute walking distance")
                           ),".")

title_text <- paste("Kitsap County",b_name)
subtitle_text <- ifelse(b_name %ni% c("Commissioner Districts","LAMIRDs"),
                        "only showing the unincorporated county","")
caption_text <- paste("Data source:",breakdowns$data_source[i])

@@

```{r bdmap-{{i}}}
#| fig.width = 8,
#| fig.height = 8,
#| out.width = '100%',
#| dpi = 96
#| 
kitsap +
  geom_sf(data = b_polydf, aes(fill = eval(as.symbol(b_idcol))), 
          lwd = 0, alpha = 0.6) +
  {if (has_points) geom_sf(data = b_pointdf, aes(color = 1), 
                           color = "black", show.legend = FALSE) } +
  theme_void() +
  labs(title = title_text,
       #subtitle = subtitle_text,
       caption = caption_text,
       fill = b_name)

@@

```{r bdloop-{{i}}, include=FALSE, echo=FALSE}

expanded_child <- lapply(
  seq_along(1:length(b_items)),
    function(xrow) {
      knitr::knit_expand(file = "Child-Metrics-Geo.Rmd",
                                x = xrow )
    })

### 2022-10-31 Draft-Ped-Metrics-Example-Alternate.Rmd
many updates not tracked

sidewalks_nc <- st_intersection(sidewalks, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- st_intersection(shoulders, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

- 5 if it has a sidewalk or shoulder of adequate size (based on road classification & standards) or a sidewalk is present where a shoulder is the standard
- 3 if the sidewalk or shoulder is present and is minimum AASHTO requirement (like a 4 ft shoulder)
- 1 if the sidewalk or shoulder is present and is narrower than AASHTO (**NOTE to subcommittee - do we think we should use a 1 if there is a shoulder when there should be a sidewalk?**)
- 0 if none present or no data

@@

getSideScore <- function(standard_sidewalk, standard_shoulder,
                         sidewalk, shoulder) {
  ifelse(is.na(standard_sidewalk), # dealing with shoulder
         case_when(
           !is.na(sidewalk) ~ 5, # there is a sidewalk present when a shoulder is the standard
           shoulder >= standard_shoulder ~ 5,
           shoulder < standard_shoulder & shoulder > 4 ~ 3,
           shoulder < standard_shoulder & shoulder > 0 ~ 1,
           TRUE ~ 0
         ),
         case_when(
           sidewalk >= standard_sidewalk ~ 5,
           sidewalk < standard_sidewalk & sidewalk > 4 ~ 3,
           sidewalk < standard_sidewalk & sidewalk > 0 ~ 1,
           TRUE ~ 0
         )
  )
}

>>>>

sidewalks_nc <- st_intersection(sidewalks, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)

# SHLDR_SURF 
# ACP - paved
# BST - bituminous surface (chip seal), like paved
# GRV - gravel
# PAP - porous asphalt
shoulders_nc <- st_intersection(shoulders, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, 
         SHLDR_SURF %in% c("ACP", "BST", "PAP"), # these are the "paved" ones
         DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

- 5 if it has a sidewalk or shoulder of adequate size (based on road classification & standards) or a sidewalk is present where a shoulder is the standard
- 3 if the sidewalk or shoulder is present and is minimum AASHTO requirement (like a 4 ft shoulder)
- *change in alternate* 2 if a shoulder is present of adequate width when a sidewalk should be present (based on road classification & standards)
- *change in alternate* 1 if there is any sidewalk or shoulder but not wide enough
- 0 if none present or no data

@@

getSideScore <- function(standard_sidewalk, standard_shoulder,
                         sidewalk, shoulder) {
  ifelse(is.na(standard_sidewalk), # dealing with shoulder
         case_when(
           !is.na(sidewalk) ~ 5, # there is a sidewalk present when a shoulder is the standard
           shoulder >= standard_shoulder ~ 5,
           shoulder < standard_shoulder & shoulder > 4 ~ 3,
           shoulder < standard_shoulder & shoulder > 0 ~ 1,
           TRUE ~ 0
         ),
         case_when(
           sidewalk >= standard_sidewalk ~ 5,
           sidewalk < standard_sidewalk & sidewalk > 4 ~ 3,
           sidewalk < standard_sidewalk & sidewalk > 0 ~ 1,
           shoulder >= standard_sidewalk ~ 2, # add for shoulder exist
           shoulder < standard_sidewalk & shoulder > 0 ~ 1,
           TRUE ~ 0
         )
  )
}

### 2022-10-31 Draft-Ped-Metrics-Example_w_Gravel.Rmd
many updates not tracked

---
title: "DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report"
date: "`r Sys.Date()`"
bibliography: metrics.bib
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 3
    fig_caption: yes
---

@@

# SHLDR_SURF 
# ACP - paved
# BST - bituminous surface (chip seal), like paved
# GRV - gravel
# PAP - porous asphalt
shoulders_nc <- st_intersection(shoulders, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, 
         SHLDR_SURF %in% c("ACP", "BST", "PAP"), # these are the "paved" ones
         DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

# NOTE: Also make this a factor so that it is sorted properly!!
sw_sh_col <- scale_color_manual(values = c("Sidewalk: 3 ft"="#E41A1C",
                                           "Sidewalk: 4 ft"="#874F6F",
                                           "Sidewalk: 5 ft"="#3881B0",
                                           "Sidewalk: 8 ft"="#449B75",
                                           "Paved Shoulder: 1 ft"="#56A255",
                                           "Paved Shoulder: 2 ft"="#7E6E85",
                                           "Paved Shoulder: 3 ft"="#AC5782",
                                           "Paved Shoulder: 4 ft"="#E3712B", 
                                           "Paved Shoulder: 5 ft"="#FFA10D",
                                           "Paved Shoulder: 6 ft"="#FFE528",
                                           "Paved Shoulder: 7 ft"="#E1C62F",
                                           "Paved Shoulder: 8 ft"="#B16C29",
                                           "Paved Shoulder: 10 ft"="#C66764",
                                           "Paved Shoulder: 12 ft"="#F17EB4",
                                           "Paved Shoulder: 15 ft"="#CB8CAD",
                                           "Paved Shoulder: 17 ft"="#999999"))
nc_sw_sh$TYPE <- factor(nc_sw_sh$TYPE, levels = c("Sidewalk: 3 ft",
                                                  "Sidewalk: 4 ft",
                                                  "Sidewalk: 5 ft",
                                                  "Sidewalk: 8 ft" ,
                                                  "Paved Shoulder: 1 ft",
                                                  "Paved Shoulder: 2 ft",
                                                  "Paved Shoulder: 3 ft",
                                                  "Paved Shoulder: 4 ft", 
                                                  "Paved Shoulder: 5 ft",
                                                  "Paved Shoulder: 6 ft",
                                                  "Paved Shoulder: 7 ft",
                                                  "Paved Shoulder: 8 ft",
                                                  "Paved Shoulder: 10 ft",
                                                  "Paved Shoulder: 12 ft",
                                                  "Paved Shoulder: 15 ft",
                                                  "Paved Shoulder: 17 ft"))
```

>>>>

---
title: "DRAFT W GRAVEL! Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report"
date: "`r Sys.Date()`"
bibliography: metrics.bib
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 3
    fig_caption: yes
---

@@

# SHLDR_SURF 
# ACP - paved
# BST - bituminous surface (chip seal), like paved
# GRV - gravel
# PAP - porous asphalt
shoulders_nc <- st_intersection(shoulders, st_buffer(county_no_cities,0)) %>%
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, 
         SHLDR_SURF %in% c("ACP", "BST", "PAP", "GRV"), # these are the "paved" ones
         DISTANCE_F > 0) %>%
  mutate(LENGTH = as.integer(st_length(.)),
         TYPE = paste0("Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

# NOTE: Also make this a factor so that it is sorted properly!!
sw_sh_col <- scale_color_manual(values = c("Sidewalk: 3 ft"="#E41A1C",
                                           "Sidewalk: 4 ft"="#874F6F",
                                           "Sidewalk: 5 ft"="#3881B0",
                                           "Sidewalk: 8 ft"="#449B75",
                                           "Shoulder: 1 ft"="#56A255",
                                           "Shoulder: 2 ft"="#7E6E85",
                                           "Shoulder: 3 ft"="#AC5782",
                                           "Shoulder: 4 ft"="#E3712B", 
                                           "Shoulder: 5 ft"="#FFA10D",
                                           "Shoulder: 6 ft"="#FFE528",
                                           "Shoulder: 7 ft"="#E1C62F",
                                           "Shoulder: 8 ft"="#B16C29",
                                           "Shoulder: 10 ft"="#C66764",
                                           "Shoulder: 12 ft"="#F17EB4",
                                           "Shoulder: 15 ft"="#CB8CAD",
                                           "Shoulder: 17 ft"="#999999"))
nc_sw_sh$TYPE <- factor(nc_sw_sh$TYPE, levels = c("Sidewalk: 3 ft",
                                                  "Sidewalk: 4 ft",
                                                  "Sidewalk: 5 ft",
                                                  "Sidewalk: 8 ft" ,
                                                  "Shoulder: 1 ft",
                                                  "Shoulder: 2 ft",
                                                  "Shoulder: 3 ft",
                                                  "Shoulder: 4 ft", 
                                                  "Shoulder: 5 ft",
                                                  "Shoulder: 6 ft",
                                                  "Shoulder: 7 ft",
                                                  "Shoulder: 8 ft",
                                                  "Shoulder: 10 ft",
                                                  "Shoulder: 12 ft",
                                                  "Shoulder: 15 ft",
                                                  "Shoulder: 17 ft"))
```
